API design for machine learning software: experiences from the scikit-learn project

### 2013-06-22 paper.tex
Title :)
acknowledge my fundings
nested objects place a burden *on the user*

% working title, please change
\title{Scikit-learn: API design for machine learning}

@@

Since meta-estimators require the construction of nested objects,
the decision to implement a meta-estimator
rather than fold the behavior it implements
into existing estimators classes
is always based on a trade-off between genericity and ease of use.
Relating to the example just given,
all \sklearn classifiers are designed to do multiclass classification
and the use of the \texttt{multiclass} module
is only necessary in advanced use cases.

@@

>>>>

\title{ API design for machine learning software: experiences from the
scikit-learn project}

@@

Since meta-estimators require users to construct nested objects,
the decision to implement a meta-estimator
rather than fold the behavior it implements
into existing estimators classes
is always based on a trade-off between genericity and ease of use.
Relating to the example just given,
all \sklearn classifiers are designed to do multiclass classification
and the use of the \texttt{multiclass} module
is only necessary in advanced use cases.

@@

Lars Buitinck is a ... Gilles Louppe is a research fellow of the Fonds de la
Recherche Scientifique-FNRS (Belgium) and acknowledges its financial support.
Mathieu Blondel is a ...
